R Notebook

### 2021-07-26 Old scripts/pupil_arousal_datarmd.Rmd
Update pupil_arousal_datarmd.Rmd

# dowsample by averaging?
colnames(tmp.df4_full_stim)
tmp.df4_full_stim_downs <- tmp.df4_full_stim %>%
  group_by(ssid, tNo, timebin, trial,trialUnq)%>%
  summarise_at(c('timerezero3','pup_basCor', 'gaze_x_cor_pix', 'gaze_y_cor_pix'), 
               mean, na.rm = TRUE)

@@

# create klarger bins
tmp.df4_full_stim_downs_jun2021_with_beh

@@

tmp.df4_full_stim_downs_jun2021_with_beh$timebin2<- OneR::bin(tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, nbin = 30)

@@

# import the timecourse

>>>>

# dowsample by averaging?
colnames(tmp.df4_full_stim)

tmp.df4_full_stim_downs
tmp.df4_full_stim_downs <- tmp.df4_full_stim %>%
  group_by(ssid, tNo, timebin, trial,trialUnq)%>%
  summarise_at(c('timerezero3','pup_basCor', 'gaze_x_cor_pix', 'gaze_y_cor_pix'), 
               mean, na.rm = TRUE)

@@

# create klarger bins

tmp.df4_full_stim_downs_jun2021
tmp.df4_full_stim_downs_jun2021_with_beh

@@

tmp.df4_full_stim_downs_jun2021_with_beh$timebin2 <- OneR::bin(tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, nbin = 30)

@@

# import the timecourse
unique(tmp.df4_full_stim_downs_jun2021)

tmp.df4_full_stim_downs_jun2021_with_beh2$
